---
title: "AUMCF Simulations (Zero frailty Variance)"
output:
  html_document: default
  pdf_document: default
date: "2025-05-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r}
setwd('~/Documents/GitHub/AUMCF_Sim')
rm(list = ls())

# Packages.
library(optparse)
library(MCC)
library(parallel)
library(dplyr)

source("JACC_methods.R")
my_reps <- 5
```

In all scenarios, the recurrent event is generated from a Poisson process with event rate of 1 in group 1 and either 1 or 1.4 in the Null and Non-Null settings, respectively. The terminal event was generated from an exponential distribution with a rate of 0.2 in both groups 1 and 2 and the censoring time was generated independently from an exponential distribution. In this set of simulations, the frailty variance was set to 0.

We varied the time to follow-up (tau = 1, 4) and censoring rate (rate = 0.2, 0.4) for a total of 4 scenarios. 

# Scenario A:  Censoring = 0.2, tau = 4 

```{r}
summarize_results <- function(sim_augmented){
  cbind(sim_augmented %>%
          group_by(type) %>%
          summarise(Pt_est = mean(value, na.rm = TRUE)),
        sim_augmented %>%
          group_by(type) %>%
          summarise(Prob_reject_H0 = mean(p_value < 0.05, na.rm = TRUE)), 
        sim_augmented %>%
          group_by(type) %>%
          summarise(ASE = mean(se, na.rm = TRUE)),
        sim_augmented %>%
          group_by(type) %>%
          summarise(ESE = sd(value, na.rm = TRUE)),
        sim_augmented %>%
          group_by(type) %>%
          summarize(n_NA = sum(is.na(value) | is.na(se) | is.na(p_value)))
  )[, -c(3,5,7,9)]
}
```

## A1: Null 
```{r results='hide'}
params <- list(
  n = 100,
  time = 4,
  censor = 0.2,
  frailtyVar = 0,
  BaseDeath0 = 0.2,
  BaseDeath1 = 0.2,
  BaseEvent0 = 1.0,
  BaseEvent1 = 1.0,
  BetaDeath = 0,
  BetaEvent = 0,
  reps = my_reps,
  adjusted = 0,
  tvr = 1.2,
  tvd = 0.2,
  experiment = 3,
  out = "Test/"
)
# Option parsing.
t0 <- proc.time()
# Output stem.
out_suffix <- paste0(
  "N", params$n, 
  "_T", params$time,
  "_l0", params$BaseEvent0,
  "_l1", params$BaseEvent1,
  "_adj", params$adjusted,
  ".rds"
)

source('test_sim_comparison.R')
```

```{r}
print(dim(sim_augmented)) 
print(summarize_results(sim_augmented))
```


## A2: Non-null (1.4)
```{r results='hide'}
params <- list(
  n = 100,
  time = 4,
  censor = 0.2,
  frailtyVar = 0,
  BaseDeath0 = 0.2,
  BaseDeath1 = 0.2,
  BaseEvent0 = 1.4,
  BaseEvent1 = 1.0,
  BetaDeath = 0,
  BetaEvent = 0,
  reps = my_reps,
  adjusted = 0,
  tvr = 1.2,
  tvd = 0.2,
  experiment = 2,
  out = "Test/"
)
# Option parsing.
t0 <- proc.time()
# Output stem.
out_suffix <- paste0(
  "N", params$n, 
  "_T", params$time,
  "_l0", params$BaseEvent0,
  "_l1", params$BaseEvent1,
  "_adj", params$adjusted,
  ".rds"
)

source('test_sim_comparison.R')
```

```{r}
print(dim(sim_augmented)) 
print(summarize_results(sim_augmented))
```

\newpage

# Scenario B:  Censoring = 0.4, tau = 4 

## B1: Null 
```{r results='hide'}
params <- list(
  n = 100,
  time = 4,
  censor = 0.4,
  frailtyVar = 0,
  BaseDeath0 = 0.2,
  BaseDeath1 = 0.2,
  BaseEvent0 = 1.0,
  BaseEvent1 = 1.0,
  BetaDeath = 0,
  BetaEvent = 0,
  reps = my_reps,
  adjusted = 0,
  tvr = 1.2,
  tvd = 0.2,
  experiment = 3,
  out = "Test/"
)
# Option parsing.
t0 <- proc.time()
# Output stem.
out_suffix <- paste0(
  "N", params$n, 
  "_T", params$time,
  "_l0", params$BaseEvent0,
  "_l1", params$BaseEvent1,
  "_adj", params$adjusted,
  ".rds"
)

source('test_sim_comparison.R')
```

```{r}
print(dim(sim_augmented)) 
print(summarize_results(sim_augmented))
```


## B2: Non-null (1.4)
```{r results='hide'}
params <- list(
  n = 100,
  time = 4,
  censor = 0.4,
  frailtyVar = 0,
  BaseDeath0 = 0.2,
  BaseDeath1 = 0.2,
  BaseEvent0 = 1.4,
  BaseEvent1 = 1.0,
  BetaDeath = 0,
  BetaEvent = 0,
  reps = my_reps,
  adjusted = 0,
  tvr = 1.2,
  tvd = 0.2,
  experiment = 2,
  out = "Test/"
)
# Option parsing.
t0 <- proc.time()
# Output stem.
out_suffix <- paste0(
  "N", params$n, 
  "_T", params$time,
  "_l0", params$BaseEvent0,
  "_l1", params$BaseEvent1,
  "_adj", params$adjusted,
  ".rds"
)

source('test_sim_comparison.R')
```

```{r}
print(dim(sim_augmented)) 
print(summarize_results(sim_augmented))
```

\newpage
# Scenario C:  Censoring = 0.2, tau = 1 

## C1: Null 
```{r results='hide'}
params <- list(
  n = 100,
  time = 1,
  censor = 0.2,
  frailtyVar = 0,
  BaseDeath0 = 0.2,
  BaseDeath1 = 0.2,
  BaseEvent0 = 1.0,
  BaseEvent1 = 1.0,
  BetaDeath = 0,
  BetaEvent = 0,
  reps = my_reps,
  adjusted = 0,
  tvr = 1.2,
  tvd = 0.2,
  experiment = 3,
  out = "Test/"
)
# Option parsing.
t0 <- proc.time()
# Output stem.
out_suffix <- paste0(
  "N", params$n, 
  "_T", params$time,
  "_l0", params$BaseEvent0,
  "_l1", params$BaseEvent1,
  "_adj", params$adjusted,
  ".rds"
)

source('test_sim_comparison.R')
```

```{r}
print(dim(sim_augmented)) 
print(summarize_results(sim_augmented))
```


## C2: Non-null (1.4)
```{r results='hide'}
params <- list(
  n = 100,
  time = 1,
  censor = 0.2,
  frailtyVar = 0,
  BaseDeath0 = 0.2,
  BaseDeath1 = 0.2,
  BaseEvent0 = 1.4,
  BaseEvent1 = 1.0,
  BetaDeath = 0,
  BetaEvent = 0,
  reps = my_reps,
  adjusted = 0,
  tvr = 1.2,
  tvd = 0.2,
  experiment = 2,
  out = "Test/"
)
# Option parsing.
t0 <- proc.time()
# Output stem.
out_suffix <- paste0(
  "N", params$n, 
  "_T", params$time,
  "_l0", params$BaseEvent0,
  "_l1", params$BaseEvent1,
  "_adj", params$adjusted,
  ".rds"
)

source('test_sim_comparison.R')
```

```{r}
print(dim(sim_augmented)) 
print(summarize_results(sim_augmented))
```

\newpage

# Scenario D:  Censoring = 0.4, tau = 1

## D1: Null 
```{r results='hide'}
params <- list(
  n = 100,
  time = 1,
  censor = 0.4,
  frailtyVar = 0,
  BaseDeath0 = 0.2,
  BaseDeath1 = 0.2,
  BaseEvent0 = 1.0,
  BaseEvent1 = 1.0,
  BetaDeath = 0,
  BetaEvent = 0,
  reps = my_reps,
  adjusted = 0,
  tvr = 1.2,
  tvd = 0.2,
  experiment = 3,
  out = "Test/"
)
# Option parsing.
t0 <- proc.time()
# Output stem.
out_suffix <- paste0(
  "N", params$n, 
  "_T", params$time,
  "_l0", params$BaseEvent0,
  "_l1", params$BaseEvent1,
  "_adj", params$adjusted,
  ".rds"
)

source('test_sim_comparison.R')
```

```{r}
print(dim(sim_augmented)) 
print(summarize_results(sim_augmented))
```


## D2: Non-null (1.4)
```{r results='hide'}
params <- list(
  n = 100,
  time = 1,
  censor = 0.4,
  frailtyVar = 0,
  BaseDeath0 = 0.2,
  BaseDeath1 = 0.2,
  BaseEvent0 = 1.4,
  BaseEvent1 = 1.0,
  BetaDeath = 0,
  BetaEvent = 0,
  reps = my_reps,
  adjusted = 0,
  tvr = 1.2,
  tvd = 0.2,
  experiment = 2,
  out = "Test/"
)
# Option parsing.
t0 <- proc.time()
# Output stem.
out_suffix <- paste0(
  "N", params$n, 
  "_T", params$time,
  "_l0", params$BaseEvent0,
  "_l1", params$BaseEvent1,
  "_adj", params$adjusted,
  ".rds"
)

source('test_sim_comparison.R')
```

```{r}
print(dim(sim_augmented)) 
print(summarize_results(sim_augmented))
```

